prolfqua - An R-package for Proteomics Differential Expression Analysis.

### 2022-05-05 inst/MyArticle/paper.Rmd
change order of code

## plotting panels
pl <- lfqd$get_Plotter()
panelA <- pl$intensity_distribution_density() +
  ggplot2::labs(tag = "A") + ggplot2::theme(legend.position = "none")

## infer protein intensities from peptide intens
agr <- lfqd$get_Aggregator()
lfqp <- agr$medpolish()

## plotting
panelB <- agr$plot()$plots[[1]] + ggplot2::labs(tag = "B")
panelC <- lfqp$get_Stats()$violin() + ggplot2::labs(tag = "C")
pl <- lfqp$get_Plotter()
panelD <- pl$boxplots()$boxplot[[1]] + ggplot2::labs(tag = "D")
ggpubr::ggarrange(panelA, panelB, panelC, panelD)
```

>>>>

## infer protein intensities from peptide intensity
agr <- lfqd$get_Aggregator()
lfqp <- agr$medpolish()

## plotting panels A-D
pl <- lfqd$get_Plotter()
panelA <- pl$intensity_distribution_density() +
  ggplot2::labs(tag = "A") + ggplot2::theme(legend.position = "none")
panelB <- agr$plot()$plots[[1]] + ggplot2::labs(tag = "B")
panelC <- lfqp$get_Stats()$violin() + ggplot2::labs(tag = "C")
pl <- lfqp$get_Plotter()
panelD <- pl$boxplots()$boxplot[[1]] + ggplot2::labs(tag = "D")
ggpubr::ggarrange(panelA, panelB, panelC, panelD)
```
